Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-21 aistats.tex
Move duality at the end of self-concordance

\begin{proposition}
	\label{prop:conjugateConcordance}
	Let $f:\real \rightarrow \real$ be a self-concordant function of Legendre type. Then its convex conjugate $f^*$ is also self-concordant.
\end{proposition}
\begin{proof}
When $f$ is of Legendre type then its convex conjugate $f^*(y) = \max_x \langle x, y \rangle - f(x)$ has inverse gadients
\begin{align}
    \nabla f \circ \nabla f^*  &= \Id \\
     \nabla f^* \circ \nabla f &= \Id
\end{align}
where $\Id$ is the identity function on the relevant domain. 
Deriving this equality proves that some Hessians are inverse of each other 
\begin{align}
    \nabla^2 f(x) \nabla^2 f^*(x^*) = \mI
    \label{eq:conjugateHessian}
\end{align}
where $(x,x^*)$ are conjugate points -- e.g. $x^*=\nabla f(x)$ and $x = \nabla f^*(x^*)$.
\TODO{Why are Hessians not 0?}
In 1 dimension, this inequality is more simply written 
\aligns{f''(x) f^{* \prime \prime}(x^*) = 1}
Until now, this should be familiar to the reader.
The interesting surprise is that self-concordance appears when we derive again this equality. 
\begin{align}
    &1= f''(x) f^{* \prime \prime}(f'(x)), \forall x \\
    \implies
    &0 = f'''(x)f^{* \prime \prime}(f'(x))  + f''(x)^2 f^{* \prime \prime \prime}(f'(x))\\
    \iff
    &0 = f'''(x)f^{* \prime \prime}(x^*)  + f''(x)^2 f^{* \prime \prime \prime}(x^*)\\
    \implies
    &0 = \frac{f'''(x)}{f''(x)^{\frac{3}{2}}}  f^{* \prime \prime}(x^*)^{-\half}
    + f''(x)^{\half} \frac{f^{* \prime \prime \prime}(x^*)}{f^{* \prime \prime}(x^*)^{\frac{3}{2}}} \\
    \implies
    &0= \frac{f'''(x)}{f''(x)^{\frac{3}{2}}}  + \frac{f^{* \prime \prime \prime}(x^*)}{f^{* \prime \prime}(x^*)^{\frac{3}{2}}}
\end{align}
where to reach the last line, we used~\eqref{eq:conjugateHessian} again.
We see that for a pair of conjugate functions, the self-concordance ratios are opposite of each other, which concludes the proof.
\end{proof}

@@

>>>>

@@

\subsection{Self-concordance and Convex Conjugates}
\begin{proposition}
	\label{prop:conjugateConcordance}
	Let $f:\real \rightarrow \real$ be a self-concordant function of Legendre type. Then its convex conjugate $f^*$ is also self-concordant.
\end{proposition}
\begin{proof}
When $f$ is of Legendre type then its convex conjugate $f^*(y) = \max_x \langle x, y \rangle - f(x)$ has inverse gadients
\begin{align}
    \nabla f \circ \nabla f^*  &= \Id \\
     \nabla f^* \circ \nabla f &= \Id
\end{align}
where $\Id$ is the identity function on the relevant domain. 
Deriving this equality proves that Hessians are inverse of each other 
\begin{align}
    \nabla^2 f(x) \nabla^2 f^*(x^*) = \mI
    \label{eq:conjugateHessian}
\end{align}
when evaluated at conjugate pairs of points $(x,x^*)$ -- e.g. $x^*=\nabla f(x)$ and $x = \nabla f^*(x^*)$.
These Hessians are never $0$.
In 1 dimension, this inequality is more simply written 
\aligns{f''(x) f^{* \prime \prime}(x^*) = 1}
Until now, this should be familiar to the reader.
The interesting surprise is that self-concordance appears when we derive again this equality. 
\begin{align}
    &1= f''(x) f^{* \prime \prime}(f'(x)), \forall x \\
    \implies
    &0 = f'''(x)f^{* \prime \prime}(f'(x))  + f''(x)^2 f^{* \prime \prime \prime}(f'(x))\\
    \iff
    &0 = f'''(x)f^{* \prime \prime}(x^*)  + f''(x)^2 f^{* \prime \prime \prime}(x^*)\\
    \implies
    &0 = \frac{f'''(x)}{f''(x)^{\frac{3}{2}}}  f^{* \prime \prime}(x^*)^{-\half}
    + f''(x)^{\half} \frac{f^{* \prime \prime \prime}(x^*)}{f^{* \prime \prime}(x^*)^{\frac{3}{2}}} \\
    \implies
    &0= \frac{f'''(x)}{f''(x)^{\frac{3}{2}}}  + \frac{f^{* \prime \prime \prime}(x^*)}{f^{* \prime \prime}(x^*)^{\frac{3}{2}}}
\end{align}
where to reach the last line, we used~\eqref{eq:conjugateHessian} again.
We see that for a pair of conjugate functions, the self-concordance ratios are opposite of each other, which concludes the proof.
\end{proof}
